### 2016-12-14 doc/paper/paper.tex
work in progress

\documentclass{sig-alternate}
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{algorithmic}
\usepackage[linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

@@

%% --------------------------------------------------------------------
\section{Test Generation Framework}
\label{sec.framework}
%% --------------------------------------------------------------------

\begin{figure}
  \centering 
  \begin{sequencediagram}[font=\scriptsize]
    \newinst{user}{User}
    \newinst{server}{Server}
    \newinst{validator}{Validator}
    \newinst{client}{Client}

    \begin{call}{user}{file.js + config}{server}{\textbf{end}}
      \begin{call}{server}{Initialize(file.js, config)}{server}{cfg, branches, cinfo, ifun, sig}
      \end{call}

@@

      \begin{sdblock}{Genetic Loop}{$\text{branch} \in \text{branches}'$}
        \begin{sdblock}{Random Loop}{errors > 0}
          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
          \end{call}
        \end{sdblock}

@@

          \begin{sdblock}{Evaluation Loop}{p $\in$ pop}
            \begin{call}{server}{POST /genetic \{p\}}{client}{response}
            \end{call}

            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
            \end{callself}
          \end{sdblock}

          \begin{sdblock}{Crossover Loop}{errors > 0}
            \begin{call}{server}{cross = Crossover(pop)}{validator}{errors}
            \end{call}
          \end{sdblock}

          \begin{sdblock}{Mutation Loop}{errors > 0}
            \begin{call}{server}{mut=Mutation(cinfo, pop)}{validator}{errors}
            \end{call}
          \end{sdblock}
        \end{sdblock}
        \mess{server}{}{user}
      \end{sdblock}
    \end{call}
  \end{sequencediagram}
  \caption{Architecture of the test generation framework}
  \label{fig.framework.architect} 
\end{figure}

\begin{algorithm}[!t]
  \caption{Initialization Phase}
  \label{alg.init}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Input{
    $fun.js$ is a JS file with FUT and type annotation
  }
  \Output{
    tuple with $(cfg, branches, cinfo)$
  }
  \Fn{$Initialize(fun.js)$}{
    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\;
    $ast' \longleftarrow TransAST(ast)$\;
    $cfg \longleftarrow BuildCFG(ast')$\;
    $branches \longleftarrow GetBranches(ast')$\;
    $cinfo \longleftarrow GetConstInfo(ast')$\;
    $ifun \longleftarrow Instrument(ast')$\;
    $Send(POST, /init, \{ifun, sig\})$\;
    \Return{$(cfg, branches, cinfo)$}
  }
\end{algorithm}

\begin{algorithm}[!t]
  \caption{Genetic Phase}
  \label{alg.init}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Fn{$Genetic(b_N, cfg, cinfo, config)$}{
    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\;
    $archive \longleftarrow \emptyset$\;
    $i \longleftarrow 0 $\;
    $pop \longleftarrow Random(cinfo, size_P)$\;
    \Repeat{$isPerfect(f^*) \vee i > size_G $}{
      $scoredPop \longleftarrow \emptyset$\;
      \ForAll{$p \in pop$}{
        $(tr, d_B, d_L, consts) \longleftarrow Send(POST, /genetic, \{p\})$\;
        \tcp{evaluate $ifun(p: sig)$}
        $(f, p) \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\;
        $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
        $cinfo \longleftarrow consts \cup cinfo$\;
      }
      $combo \longleftarrow scoredPop \cup archive$\;
      $cross \longleftarrow Crossover(combo, rate_C)$\;
      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\;
      $pop \longleftarrow cross \cup mut$\;
      $archive \longleftarrow GetBest(combo, size_A)$\;
      $(f^*, p^*) \longleftarrow head(archive)$\;
      $i \longleftarrow i + 1$\;
    }
    \Return{$(f^*, p^*)$} 
  }
\end{algorithm}

The general structure of the JavaScript test generation framework is depicted in Figure~\ref{fig.framework.architect}. It consists of three main components

>>>>

\documentclass{sig-alternate}
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{algorithmic}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}

@@

%% --------------------------------------------------------------------
\section{Test Generation Framework}
\label{sec.framework}
%% --------------------------------------------------------------------
The general workflow of our JavaScript test generation framework is represented as a sequence diagram in Figure~\ref{fig.framework.architect}. The diagram consists of four interacting components: \User, \Server\, \Validator and \Client, where \Server is the main one. It performs all preparatory steps (\emph{Initialization Phase}) as well as controls the data generation (\emph{Genetic Phase}). These two phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.

Every request sent to \Validator\footnote{\url{https://validator.w3.org/nu/}} with an HTML document as the body triggers a response containing the list of syntactic errors in that document. \Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JavaScript code. It relies on the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to simulate calls to native DOM.

Let us get a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}. First, \User provides JS file (\emph{file.js}) that contains the function under test (FUT) together with its type and a configuration file \emph{config}. These data are processed by the \Server in the \emph{Initialization Phase}. As an output we get a tuple with the following information about FUT: control flow graph (\emph{cfg}), list of branches (\emph{branches}), static information about the program's constants (\emph{cinfo}), instrumented version of the original program (\emph{ifun}) and the function's signature (\emph{sig}). \Server sends a \texttt{POST} request to the \Client to store \emph{ifun} and \emph{sig}. Second, \Server asks \User to select a branch(s) that has to be covered by the execution of FUT. For each branch our framework triggers the \emph{Genetic Phase (Loop)}. Inside of this phase it starts with a randomly generated population (\emph{Random Loop}), and continues to improve it until earthier perfect value is found or generation limit is reached. Each candidate in the population has to be evaluated. \Client parses the candidate according the know signature, invokes \emph{ifun} on the result, collects some information along the execution and sends it back to \Server, where the final fitness value is computed for that candidate (\emph{Evaluation Loop}). New population is the formed as joint result of the \emph{Crossover} and \emph{Mutation Loop}. At the end of the \emph{Fitness Loop} the best candidate with the best fitness value is reported to \User. After exhausting all branches \emph{Genetic Loop} terminates.

\begin{figure}
  \centering 
  \begin{sequencediagram}[font=\scriptsize]
    \newinst{user}{User}
    \newinst{server}{Server}
    \newinst[1]{validator}{Validator}
    \newinst{client}{Client}

    \begin{call}{user}{file.js + config}{server}{\textbf{end}}
      \begin{call}{server}{Initialize(file.js, config)}{server}{(cfg, branches, cinfo, ifun, sig)}
      \end{call}

@@

      \begin{sdblock}{Genetic Loop}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
        \begin{sdblock}{Random Loop}{errors > 0}
          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
          \end{call}
          \prelevel
        \end{sdblock}

@@

          \begin{sdblock}{Evaluation Loop}{p $\in$ pop}
            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
            \end{call}

            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
            \end{callself}
            \prelevel
          \end{sdblock}

          \begin{sdblock}{Crossover Loop}{errors > 0}
            \begin{call}{server}{cross = Crossover(pop)}{validator}{errors}
            \end{call}
            \prelevel
          \end{sdblock}

          \begin{sdblock}{Mutation Loop}{errors > 0}
            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
            \end{call}
            \prelevel
          \end{sdblock}

          \begin{callself}{server}{cross $\cup$ mut}{pop}
          \end{callself}
          \prelevel
        \end{sdblock}
        \mess{server}{best fitness}{user}

      \end{sdblock}
    \end{call}
  \end{sequencediagram}
  \caption{Architecture of the test framework}
  \label{fig.framework.architect} 
\end{figure}

\begin{algorithm}[t!]
  \caption{Initialization Phase}
  \label{alg.init}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Input{
    $fun.js$ is a JS file with FUT and type annotation
  }
  \Output{
    tuple with $(cfg, branches, cinfo)$
  }
  \Fn{$Initialize(fun.js)$}{

    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\label{alg1.parse.fun.sig}\;
    $ast' \longleftarrow TransAST(ast)$\;
    $cfg \longleftarrow BuildCFG(ast')$\;
    $branches \longleftarrow GetBranches(ast')$\;
    $cinfo \longleftarrow GetConstInfo(ast')$\;
    $ifun \longleftarrow Instrument(ast')$\;
    $Send(POST, /init, \{ifun, sig\})$\;
    \Return{$(cfg, branches, cinfo)$}
    }
\end{algorithm}

\begin{algorithm}[!t]
  \caption{Genetic Phase}
  \label{alg.gen}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Fn{$Genetic(b_N, cfg, cinfo, config)$}{
    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\;
    $archive \longleftarrow \emptyset$\;
    $i \longleftarrow 0 $\;
    $pop \longleftarrow Random(cinfo, size_P)$\;
    \Repeat{$isPerfect(f^*) \vee i > size_G $}{
      $scoredPop \longleftarrow \emptyset$\;
      \ForAll{$p \in pop$}{
        $(tr, d_B, d_L, consts) \longleftarrow Send(POST, /genetic, \{p\})$\;
        \tcp{evaluate $ifun(p: sig)$}
        $(f, p) \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\;
        $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
        $cinfo \longleftarrow consts \cup cinfo$\;
      }
      $combo \longleftarrow scoredPop \cup archive$\;
      $cross \longleftarrow Crossover(combo, rate_C)$\;
      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\;
      $pop \longleftarrow cross \cup mut$\;
      $archive \longleftarrow GetBest(combo, size_A)$\;
      $(f^*, p^*) \longleftarrow head(archive)$\;
      $i \longleftarrow i + 1$\;
    }
    \Return{$(f^*, p^*)$} 
  }
\end{algorithm}
